Overview of the eHealth Knowledge Discovery Challenge at IberLEF 2021

### 2021-06-18 paper/paper.tex
Update

\documentclass[a4paper,11pt,twocolumn,twoside]{article}
\usepackage[dvips]{graphicx}
\usepackage{sepln_en}
\usepackage{fullname}
\usepackage[utf8]{inputenc}
\usepackage[spanish,es-nosectiondot, es-tabla, es-noindentfirst, es-nolists]{babel}

@@

\title{Título completo del artículo centrado con Times New Roman negrita, tamaño 16}

@@

\seplntranstitle{Título traducido del artículo centrado con Times New Roman negrita, cursiva, tamaño 14}

@@

\section{Título de nivel uno}

\cite{piad2019general}

\section*{Agradecimientos}

>>>>

\documentclass[a4paper,11pt,twocolumn,twoside]{article}
\usepackage[dvips]{graphicx}
\usepackage{sepln_en}
\usepackage{fullname}
\usepackage[utf8]{inputenc}
% \usepackage[spanish,es-nosectiondot, es-tabla, es-noindentfirst, es-nolists]{babel}

@@

\title{Overview of the eHealth Knowledge Discovery Challenge at IberLEF 2021}

@@

\seplntranstitle{Resumen de la Tarea de Descubrimiento de Conocimiento en Salud en IberLEF 2021}

@@

\section{Introduction}

The vast amount of knowledge stored in natural language

How many pieces of knowledge are unconnected, and could lead to new discoveries,
drug repositioning, trying new medication, finding causes for diseases, just
by connecting facts and claims in different sources.

Discovering knowledge from text requires assigning a semantic interpretation
to the text that can be later converted to a data structure (e.g., ontology)

The first step is detect the relevant concepts, or entities mentioned, and how
they relate to each other

The importance of multi-domain and multi-lingual approaches

Motivation of the challenge

Motivation of the design of a custom annotation schema that is less complex
than e.g., AMR but still has some formal semantics

Importance of working in low-resource languages and with scarse training data,
to encourage transfer learning, unsupervised learning, and low cost solutions

\section{Tasks Descriptions}

The eHealth-KD challenge consists on the automatic sentence-level annotation
of multi-token entities and binary relations among them.

A custom annotation model has been defined, comprising 4 entity types and 13 relations,
that attempts to capture a large part of factual semantics in technical documents,
including enciclopedias, news, and scientific papers.

The annotation model is explained in detail in \namecite{piad2019general}.

A brief explanation is presented next.

-- Explicar las entidades y relaciones como siempre.

The challenge has been divided into two different subtasks:
entity recognition and relation extraction.

To evaluate each subtask, we count correct, partial, missing, and spurious
annotations, and weight them according to an $F_1$ measure, independently per task.

-- Fórmulas

Furthermore, the challenge is graded in three different scenarios:
one for each subtask and one where both subtasks are performed in sequence.
This is the main scenario, which ultimately decides the winner of the challenge,
although all other results are interesting.

\section{Corpora and Resources}

The Challenge is based on a corpus of documents composed of
sentences taken from previous challenges and other resources,
and newly annotated sentences.

Three different sources of textual information are sampled: medline articles,
wikinews articles, and biomedical papers from the CORD-19 corpus.

The medline and wikinews articles are in Spanish, while CORD are in English.

From the 2019 and 2020 challenges, X sentences where taken.

For this new edition, Y sentences were annotated by a team of annotators.
The team composition is 4 junior annotators and 3 senior annotators.
2 junior annotators annotated each sentence, and a senior annotator performed the merging.

The newly annotated sentences are used solely for evaluation purposes,
while all training and development resources are reused from previous challenges.

Overall, the composition of the corpus is presented in Table~\ref{tab:corpus}.

\begin{table}
  \caption{Composition of the corpus, highlighting resources from previous
  challenges and newly annotated sentences.\label{tab:corpus}}
\end{table}

\section{Systems Descriptions}
´
The challenge caught the attention of 8 participants from across the globe,
who presented a variety of approaches clustered around deep learning architectures.

-- Describir los sistemas

\section{Challenge Results}

Table~\ref{tab:results} summarizes the main results in the challenge.

\begin{table}
  \caption{Results.\label{tab:results}}
\end{table}

In Scenario 1, the best performing system is\dots

-- Describir los demás escenarios

\section{Discussion}

-- Ver los sistemas con sus features y qué features son mejores o peores en cada tarea

-- Comparar con los baselines en cada tarea, hasta qué nivel está resuelta cada tarea

-- Hablar brevemente de la evolución de los sistemas en las 4 ediciones,
cómo se han ido moviendo hacia transformers

-- Hablar de la modelación de las entidades y relaciones como tareas separadas,
la desventaja que puede representar eso porque los sistemas que han ganado hacen
ambas cosas a la vez, o sea hay representación conjunta que es válida

-- Hablar de las relaciones como problema binario, que no tiene en cuenta que ciertas
relaciones implican posiblemente la aparición de otras.

-- Hablar de que el orden en que el humano anota no es el mismo que un sistema,
y que si se pudiera aprender algo de esto, dar con el dataset no solo las anotaciones
sino en qué orden fueron realizadas.

-- Hablar de la necesidad de cambiar de tareas hacia algo que refleje el valor
del conocimiento extraído, como question answering.

\section{Conclusions}

\section*{Acknowledgments}
